What can we learn about life in the city by mining the Melbourne’s Open Data Platform?

### 2017-05-03 thesis/proposal_draft.Rmd
thurs morning update

\begin{center}
Figure 4: Interactive data visualisation created using Tableau
\end{center}

@@

The use of weather data to improve forecasting performance would be ideal, due to the availability of weather forecasts compared to many other forms of data. Machine learning techniques will also be explored. In particular, clustering of sensor locations may be useful in identifying patterns at certain types of location, such as tourist attractions and shopping districts.

@@

Once a model for forecasting the data has been established, an interactive web application to present the model will be developed. A key aspect which we want to include is the ability for the end user to forecast pedestrian activity in the future.

>>>>

\begin{center}
Figure 4: An interactive data visualisation created using Tableau
\end{center}

@@

The use of weather data to improve forecasting performance would be ideal, due to the availability of weather forecasts compared to many other forms of data. Machine learning techniques will also be explored. In particular, clustering of sensor locations may be useful in identifying patterns at certain types of location, such as tourist attractions and shopping districts.  To evaluate the performance of the model, we look to minimise the RMSE (root mean square error):
$$ \text{RMSE} = \sqrt{\frac{\sum_{t=1}^{T}(\hat{y_t} - y_t)^2}{T}}$$

@@

Once a model for forecasting the data has been established, an interactive web application to present the model will be developed. A key aspect which we want to implement is the ability for the end user to forecast pedestrian activity in the future. Improving on the currently available visualisations, the aesthetics of the visualisation will be designed with human perception theory taken into consideration. Preattentive processing theory will be considered to ensure certain elements of the visualisation allow for quick, preattentive identification of busy and quiet areas. Change blindness theory should also be reviewed in order to avoid misperception of relative changes in pedestrian activity.
